Msigdf Biogrid" [??? Is it the right title?]

### 2019-09-14 Analysis/Normalized_Coherence.Rmd
More bugs ???

```{r}  
[??? What those functions do?]
source("./functions/disease2frame.R") 
source("./functions/GeneSample.R")
source("./functions/get_msig_slopes.R")

@@

get_msig_slopes = function(sub_cats, database) {
  require(msigdbr)
  msig = msigdbr()

@@

>>>>

```{r}  
[??? What those functions do?]
source("./functions/disease2frame.R") 
source("./functions/GeneSample.R")
source("./functions/get_msig_slopes.R") [??? This does not exist!]

@@

get_msig_slopes = function(sub_cats, database) { [??? Calls to this function use "subcat", not "sub_cat" argument - correct]
  require(msigdbr)
  msig = msigdbr()

@@

[??? After hacking around, normalized coherence objects still contain data for ONE disease, not many. What is going on?]
